Paper 2: Vitamin D

### 2017-10-12 doc/vitaminD.Rmd
fixed gee scaling (percent change)

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UrinaryCalcium",
           "UDBP",
           "udbpCrRatio",
           "VitaminD",
           "PTH",
           "MET",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "diet_milk",
           "diet_cal",
           "diet_supp_cal",
           "diet_supp_vitd",
           "OralContraceptive",
           "dmStatus"),
  strata = c("vitdStatus"),
  data = dsBase,
  factorVars = c("Sex", "Ethnicity", "OralContraceptive", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "ACR",
                      "UrineMicroalbumin"),
        quote = FALSE,
        noSpaces = TRUE) %>% 
  knitr::kable()
```

@@

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "MET",
           "VitaminD",
           "PTH",
           "UDBP",
           "udbpCrRatio",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "OralContraceptive",
           "dmStatus"),
  strata = c("fVN"),
  data = ds,
  factorVars = c("Sex", "Ethnicity", "OralContraceptive", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "udbpCrRatio"),
        quote = FALSE,
        noSpaces = TRUE) %>% 
  knitr::kable()

@@

# Clean data
vitd <- ds %>% 
  filter(fVN == "Baseline") %>% 
  select(vitdStatus, udbpCrRatio) %>%
  na.omit()

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(udbpCrRatio)", 
            "Vitamin D Status",
            "log uVDBP:Creatinine (μg/mmol)")

# value
vitd %>%
  dplyr::group_by(vitdStatus) %>% 
  dplyr::summarise(Median = median(log(udbpCrRatio)), 
                   IQR = IQR(log(udbpCrRatio))
                   )

@@

# ANOVA
anova <- aov(formula = log(udbpCrRatio)~vitdStatus, data = vitd)
summary(anova)
TukeyHSD(anova)
rm(anova)
```

@@

dsBase %>% 
  scatter_plot("log(udbpCrRatio)", "VitaminD", 
               "log UDBP:Creatinine",
               "Serum 25(OH)D")

@@

dsBase %>% 
  cor.test(formula = ~ VitaminD + udbpCrRatio, data = ., method = "spearman")

@@

dsBase %>% 
  prep_mason_data() %>% 
  mason_glm(y = "VitaminD",
            x = "logudbpCrRatio",
            covars = c("ageBase", "Sex", "Ethnicity", "BMI", "MET", "fDM")
            ) %>% 
  dplyr::filter(!term == "(Intercept)") %>%
  dplyr::mutate(p = round(p.value, 2),
    p = ifelse(p == "0", "<0.001", p),
    estCI = paste0(round(estimate, 2), " (",
                               round(conf.low, 2), ", ",
                               round(conf.high, 2), ")")) %>% 
  dplyr::select(Yterms, Xterms, term, estCI, p) %>% 
  # tidyr::spread(Yterms, estCI) %>%
  pander::pander()

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_gee(y = c("VitaminD", "PTH"),
            x = "udbpBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = c("VitaminD", "PTH"),
            x = "udbpBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", 
                       "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

dsBase %>% 
  interac_plot(yvar = "PTH",
               intvar = "Season",
               ylab = "Parathyroid Hormone (pmol/L)") #Serum 25(OH)D (nmol/L) #Parathyroid Hormone (pmol/L)

rms::ols(VitaminD ~ udbpCrRatio * Season, data = dsBase)
```

@@

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_gee(y = c("VitaminD", "PTH"),
            x = "UDBP",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

gee_vitd %>% 
  dplyr::filter(!term == "(Intercept)") %>% 
  dplyr::mutate(p = round(p.value, 2),
    p = ifelse(p == "0", "<0.001", p),
    estCI = paste0(round(estimate, 2), " (",
                               round(conf.low, 2), ", ",
                               round(conf.high, 2), ")")) %>% 
  dplyr::select(Yterms, Xterms, term, estCI, p) %>% 
  # tidyr::spread(Yterms, estCI) %>%
  pander::pander()

@@

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = c("VitaminD", "PTH"),
            x = "UDBP",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

ds %>% 
  interac_plot(yvar = "VitaminD",
               intvar = "Season",
               ylab = "Serum 25(OH)D (nmol/L)")

rms::ols(VitaminD ~ udbpCrRatio * Season, data = ds)
```

>>>>

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UrinaryCalcium",
           "UDBP",
           "udbpCr",
           "VitaminD",
           "PTH",
           "MET",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "diet_milk",
           "diet_cal",
           "diet_supp_cal",
           "diet_supp_vitd",
           "dmStatus"),
  strata = c("vitdStatus"),
  data = dsBase,
  factorVars = c("Sex", "Ethnicity", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "ACR",
                      "UrineMicroalbumin"),
        quote = FALSE,
        noSpaces = TRUE) %>% 
  knitr::kable()
```

@@

# for sensitivity analysis
m <- ds %>% 
  dplyr::filter(fVN != "6Year")

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "MET",
           "VitaminD",
           "PTH",
           "UDBP",
           "udbpCr",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "dmStatus"),
  strata = c("VN"),
  data = m,
  factorVars = c("Sex", "Ethnicity", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "udbpCr"),
        quote = FALSE,
        noSpaces = TRUE) %>% 
  knitr::kable()

@@

# Clean data
vitd <- ds %>% 
  filter(fVN == "Baseline") %>% 
  select(vitdStatus, udbpCr) %>%
  na.omit()

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:Creatinine (μg/mmol)")

# value
vitd %>%
  dplyr::group_by(vitdStatus) %>% 
  dplyr::summarise(Median = median(log(udbpCr)), 
                   IQR = IQR(log(udbpCr))
                   )

@@

# ANOVA
anova <- aov(formula = log(udbpCr)~vitdStatus, data = vitd)
summary(anova)
TukeyHSD(anova)
rm(anova)
```

@@

dsBase %>% 
  scatter_plot("log(udbpCr)", "VitaminD", 
               "log UDBP:Creatinine",
               "Serum 25(OH)D")

@@

dsBase %>% 
  cor.test(formula = ~ VitaminD + udbpCr, data = ., method = "spearman")

@@

dsBase %>% 
  prep_mason_data() %>% 
  mason_glm(y = "VitaminD",
            x = "logudbpCr",
            covars = c("ageBase", "Sex", "Ethnicity", "BMI", "MET", "fDM")
            ) %>% 
  dplyr::filter(!term == "(Intercept)") %>%
  dplyr::mutate(p = round(p.value, 2),
    p = ifelse(p == "0", "<0.001", p),
    estCI = paste0(round(estimate, 2), " (",
                               round(conf.low, 2), ", ",
                               round(conf.high, 2), ")")) %>% 
  dplyr::select(Yterms, Xterms, term, estCI, p) %>% 
  # tidyr::spread(Yterms, estCI) %>%
  pander::pander()

@@

# gee_vitd_baseline <- ds %>% 
#   prep_mason_data_vitd() %>% 
#   mason_gee(y = c("VitaminD", "PTH"),
#             x = "udbpCrBase",
#             covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
#             intvar = "Season") %>% 
#   mason::polish_renaming(rename_gee_vitd)

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = c("lVitD", "lPTH"),
            x = "udbpCrBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", 
                       "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

@@

# dsBase %>% 
#   interac_plot(yvar = "PTH",
#                intvar = "Season",
#                ylab = "Parathyroid Hormone (pmol/L)") #Serum 25(OH)D (nmol/L) #Parathyroid Hormone (pmol/L)
# 
# rms::ols(VitaminD ~ udbpCr * Season, data = dsBase)
```

@@

# gee_vitd <- ds %>% 
#   prep_mason_data_vitd() %>% 
#   mason_gee(y = c("lVitD", "lPTH"),
#             x = "udbpCr",
#             covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
#             intvar = "Season") %>% 
#   mason::polish_renaming(rename_gee_vitd)

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = c("lVitD", "lPTH"),
            x = "udbpCr",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

gee_vitd %>% 
  gee_results_table() %>% 
  # tidyr::spread(Yterms, estCI) %>%
  pander::pander()

@@

@@

# ds %>% 
#   interac_plot(yvar = "VitaminD",
#                intvar = "Season",
#                ylab = "Serum 25(OH)D (nmol/L)")
# 
# rms::ols(VitaminD ~ udbpCr * Season, data = ds)
```
